Deciding to Disclose

### 2016-09-30 Introduction.tex

The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

>>>>

The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2016-09-30 SensitivityAnalysis.tex
Missing table line
Renaming sections

%!TEX root = disclosure_game.tex
%Include the descent into chaos bit
\section{Sensitivity Analysis}
\label{app:sensitivity_results}

@@

\subsection{Median Moderate Drinker Signalling}

\begin{table}[H]
\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\
Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\
Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\
\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{top_5_table_sig}

\subsection{Median Between Groups IQR}

\begin{table}[H]
\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\
\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\
\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\
\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\
\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\
\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\
Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\
Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\
Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\
\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{top_5_table_group_iqr}

\subsection{Median Moderate Drinker Signalling IQR}

\begin{table}[H]
\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\
\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\
\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\
\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\
\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\
\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\
Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\
Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\
Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\
\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{top_5_table_sig_iqr}

\subsection{Between Groups IQR IQR}

\begin{table}[H]
\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\
\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\
\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\
\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\
\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\
\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\
Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\
Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\
Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\
\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{top_5_table_group_iqr_iqr}

>>>>

%!TEX root = disclosure_game.tex
%Include the descent into chaos bit
\chapter{Sensitivity Analysis}
\label{app:sensitivity_results}

@@

\section{Median Moderate Drinker Signalling}

\begin{table}[H]
\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
\rotatebox{90}{
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\
Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
}
\end{table}

\begin{table}[H]
\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
\rotatebox{90}{
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\
Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\
\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
}
\end{table}

\input{midwives/top_5_table_sig}

\section{Median Between Groups IQR}

\begin{table}[H]
\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
\rotatebox{90}{
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\
\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\
\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\
\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\
\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\
\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\
Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
}
\end{table}

\begin{table}[H]
\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\
Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\
Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\
\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{midwives/top_5_table_group_iqr}

\section{Median Moderate Drinker Signalling IQR}

\begin{table}[H]
\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
\rotatebox{90}{
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\
\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\
\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\
\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\
\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\
\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\
Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\
Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\
Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\
\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{midwives/top_5_table_sig_iqr}

\section{Between Groups IQR IQR}

\begin{table}[H]
\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
\rotatebox{90}{
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\
\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\
\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\
\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\
\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\
\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\
Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\
Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\
Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\
\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\input{midwives/top_5_table_group_iqr_iqr}
